Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-10 draft/accordionComplexSurfaces.tex
start changing sect 6

\section{$\b{g}$-, $\b{c}$- and $\b{d}$-vectors}

@@

In this section, we recall some results from Section 4.2 of~\cite{PaluPilaudPlamondon} that immediately generalise to the case of locally gentle algebras.
We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$- vectors.

\subsection{$\b{g}$-vectors and $\b{c}$-vectors}
\label{subsec:gcvectors}

@@

\begin{definition}\label{def: g-vectors for walks}
For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
\[
\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}.
\]
For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$, and that, since for any walk~$\omega$, the strings $\omega$ and $\omega^{-1}$ are eventually direct or inverse, the coordinates of~$\gvector{\omega}$ are finite.
\end{definition}

\begin{remark}
Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let $\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
Then the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
\end{remark}

\begin{definition}\label{def: c-vectors for walks}
Let~$\omega$ be a walk in a non-kissing facet~$F \in \RNKC$.
Define
\[
\distinguishedSign{\omega}{F} \eqdef 
\begin{cases}
\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie the arrows~$\distinguishedArrows{\omega}{F}$ point outside),} \\
-1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the arrows~$\distinguishedArrows{\omega}{F}$ point inside).}
\end{cases}
\]
The \defn{$\b{c}$-vector} of a walk~$\omega$ of~$F$ is the vector~${\cvector{\omega}{F} \in \R^{Q_0}}$ defined by
\[
\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}.
\]
We let~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$ be the set of $\b{c}$-vectors of a non-kissing facet~$F \in \RNKC$, and~$\allcvectors \eqdef \bigcup_F \cvectors{F}$ be the set of all $\b{c}$-vectors of all non-kissing facets~${F \in \RNKC}$.
\end{definition}

@@

\begin{proof}
Definitions~\ref{def: c-vectors for accordions} and~\ref{def: g-vectors for slaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def: c-vectors for walks} and~\ref{def: g-vectors for walks} respectively.
\end{proof}

>>>>

\section{$\b{g}$-vectors, $\b{c}$-vectors, and $\b{d}$-vectors}

@@

In this section, we define of three relevant families of vectors associated to walks in the non-kissing complex of a locally gentle quiver~$\bar Q$.
The $\b{g}$- and $\b{c}$-vectors were already considered for gentle algebras in~\cite[Sect.~4.2]{PaluPilaudPlamondon}, and their definition immediately generalizes to the case of locally gentle algebras.
Our objective is just to provide interpretations of these vectors in terms of the surface~$\surface_{\bar Q}$.
We show that our geometric model using accordions is well-adapted to computing~$\b{c}$-vectors, while slaloms can naturally be interpreted as~$\b{g}$-vectors.

\subsection{$\b{g}$-vectors, $\b{c}$-vectors, and $\b{d}$-vectors for walks}
\label{subsec:gcdVectorsWalks}

@@

\begin{definition}
\label{def:gVectorsWalks}
For a walk~$\omega \in \NKWalks^\pm(\bar Q)$, we denote by~$\peaks{\omega}$ (resp.~by~$\deeps{\omega}$) the multiset of vertices of~$Q_0$ corresponding to the peaks (resp.~deeps) of~$\omega$.
The \defn{$\b{g}$-vector} of a walk~$\omega$ is the vector~${\gvector{\omega} \in \R^{Q_0}}$ defined by
\[
\gvector{\omega} \eqdef \multiplicityVector_{\peaks{\omega}} - \multiplicityVector_{\deeps{\omega}}.
\]
For a set~$\Omega$ of walks, we let~$\gvectors{\Omega} \eqdef \set{\gvector{\omega}}{\omega \in \Omega}$.
Observe that~$\gvector{\omega} = 0$ for a straight walk~$\omega$, and that, since for any infinite walk~$\omega$ is eventually cyclic, the coordinates of~$\gvector{\omega}$ are finite.
\end{definition}

%\begin{remark}
%\vincent{I vote for deleting this remark. This goes to the next paper. The present paper should have no algebra}
%Let~$\omega$ be a walk in~$\NKWalks^\pm(\bar Q)$, and let $\sigma$ be the string obtained from~$\omega$ by deleting a left and a right co-hook when possible.
%Then the~$\b{g}$-vector of the walk~$\omega$ coincide with the~$\b{g}$-vector of the (finitely generated) string module associated with the string~$\sigma$.
%\end{remark}

\begin{definition}
\label{def:cVectorsWalks}
Let~$\omega$ be a walk in a non-kissing facet~$F \in \RNKC$.
Define
\[
\distinguishedSign{\omega}{F} \eqdef 
\begin{cases}
\phantom{-}1 & \text{if~$\distinguishedString{\omega}{F}$ is a top substring of~$\omega$ (\ie the arrows~$\distinguishedArrows{\omega}{F}$ point outside),} \\
-1 & \text{if~$\distinguishedString{\omega}{F}$ is a bottom substring of~$\omega$ (\ie if the arrows~$\distinguishedArrows{\omega}{F}$ point inside).}
\end{cases}
\]
The \defn{$\b{c}$-vector} of a walk~$\omega$ of~$F$ is the vector~${\cvector{\omega}{F} \in \R^{Q_0}}$ defined by
\[
\cvector{\omega}{F} \eqdef \distinguishedSign{\omega}{F} \, \multiplicityVector_{\distinguishedString{\omega}{F}}.
\]
We let~$\cvectors{F} \eqdef \set{\cvector{\omega}{F}}{\omega \in F}$ be the set of $\b{c}$-vectors of a non-kissing facet~$F \in \RNKC$, and~$\allcvectors \eqdef \bigcup_F \cvectors{F}$ be the set of all $\b{c}$-vectors of all non-kissing facets~${F \in \RNKC}$.
\end{definition}

\begin{definition}
\label{def:dVectorsWalks}
\vincent{TOTO: d-vectors}
\end{definition}

\begin{example}
\label{exm:gcdVectorsWalks}
\vincent{TODO: exm g- c- and d-vectors}
\end{example}

\subsection{$\b{g}$-vectors, $\b{c}$-vectors, and~$\b{d}$-vectors on the surface}
\label{subsec:gcdVectorsSurface}

@@

\begin{proof}
Definitions~\ref{def: c-vectors for accordions} and~\ref{def: g-vectors for slaloms} are immediate translations in terms of curves on the surface~$\surface(\bar Q)$ of Definitions~\ref{def:cVectorsWalks} and~\ref{def:gVectorsWalks} respectively.
\end{proof}

\subsection{Geometric properties of these vectors}
\label{subsec:geometricProperties}
